Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-08 writeup/rocha_etal.tex
Fixes typo

An important caveat is that this study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.

>>>>

An important caveat is that this study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension. This may be a typical of mesoscale-rich
subtropical region, but it is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.
